Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Move comment around
Add more comments for @kazu

TBD: describe the implementation of {\tt shouldBe}, etc.

@@

TBD

>>>>

\begin{quote}
    sol: @kazu: Can you add the documentation of \verb|test-shouldbe|
    to the bib, and cite it here?
\end{quote}

\noindent All combinators introduced in \ref{} have been
implemented~\cite{TODO}; and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.

\begin{quote}
    TBD: The implementation of \verb|shouldThrow| may still be
    interesting.  We can describe it, if we have time left.
\end{quote}

@@

\begin{quote}
    TBD

    sol: @kazu, can you work on this, if you have time.  I think an
    ``itemized'' list is better than text.  It more flexible for now,
    and @mkl or @sol can do the final wording)
\end{quote}
